A Switching Planner for Combined Task and Observation Planning

### 2010-11-26 subarchitectures/planner.sa/trunk/src/latex/ICAPS-2011/moritz_2011.tex
new structure, and altered for n omore FSC

\section{Moritz's Initial Outline}

\subsection{Switching Planner Outline}

Outline the high level approach here:
\begin{itemize}
\item Problem input (factored initial state, DTPDDL observations)
\item Determinisation
\item Problem generation for DT
\item Belief revision
\end{itemize}

\subsection{Determinisation}

\begin{itemize}
\item Generation of deterministic sensing models
\item Determinisation of the initial state
\item Compiling reward model into (soft-)goal model
\item Cost function in FD (maybe this could mentioned in the outline?)
\end{itemize}

\subsection{Subtask Generation}
\begin{itemize}
\item Goal generation from CP trace
\item Disconfirm actions
\item State pruning according to CP trace
\end{itemize}

\subsection{Belief revision}
Not sure if this needs its own section
\begin{itemize}
\item Convert inital state into bayesian network
\item Belief updates with observation nodes
\item Create new network for next planning runs
\end{itemize}

@@

\section{Switching Planner}
\input{switching.tex}

>>>>

%% \section{Moritz's Initial Outline}

%% \subsection{Switching Planner Outline}

%% Outline the high level approach here:
%% \begin{itemize}
%% \item Problem input (factored initial state, DTPDDL observations)
%% \item Determinisation
%% \item Problem generation for DT
%% \item Belief revision
%% \end{itemize}

%% \subsection{Determinisation}

%% \begin{itemize}
%% \item Generation of deterministic sensing models
%% \item Determinisation of the initial state
%% \item Compiling reward model into (soft-)goal model
%% \item Cost function in FD (maybe this could mentioned in the outline?)
%% \end{itemize}

%% \subsection{Subtask Generation}
%% \begin{itemize}
%% \item Goal generation from CP trace
%% \item Disconfirm actions
%% \item State pruning according to CP trace
%% \end{itemize}

%% \subsection{Belief revision}
%% Not sure if this needs its own section
%% \begin{itemize}
%% \item Convert inital state into bayesian network
%% \item Belief updates with observation nodes
%% \item Create new network for next planning runs
%% \end{itemize}

@@

\section{Switching Continual Planner}
\input{switching.tex}

### 2010-11-26 subarchitectures/planner.sa/trunk/src/latex/ICAPS-2011/prop-dtp.tex
new structure, and altered for n omore FSC

We model a process state $\state$ as the set of propositions that are
true of the state. Notationally, we have $\state \subseteq
\props$. State change is induced by application of actions. A
stochastic action $\stochAction \in \stochActions$ is applicable if
its precondition $\poss(\stochAction)$, a set of propositions, are
satisfied in the current state -- I.e., $\poss(\stochAction) \subseteq
\state$. We write $\stochActions(\state)$ for set of actions
applicable at state $\state$.  If action $\stochAction \in
\stochActions(\state)$ is applied at \state, nature chooses one
element amongst a small set of deterministic outcomes
$\detActions(\stochAction) \equiv \{\detAction_1, \ldots, \detAction_k
\}$. We denote $\mu_{\stochAction}(\detAction_i)$ the probability that
nature takes outcome $\detAct_i$, and for all \stochAction\ we require
$\sum_{\detAction_i \in \detActions(\stochAction)}
\mu_{\stochAction}(\detAction_i) = 1$. The chosen outcome has an
effect on the state given in terms of two lists of propositions. The
add-list $\add(\detAction)$ and delete-list
$\delete(\detAction)$.\footnote{If a proposition is in the add-list of
$\detAction$, then it cannot be in the delete-list and vice versa.}
If outcome $\detAction$ with $\add(\detAction) := [\prop_1,
..,\prop_n]$ and $\delete(\detAction) := [\overline\prop_{n+1},
..,\overline\prop_m]$ is chosen by nature when \stochAction\ is
applied at state $\state$, then the resultant state is $ ( \state \cup
\add(\detAction) ) \backslash \delete(\detAction)$ -- i.e.,
propositions from $\add(\detAction)$ are added to $\state$, and those
from $\delete(\detAction)$ are removed from $\state$.

@@

An optimal solution to a finite-horizon POMDP is a contingent plan,
and can be expressed as a mapping from observation histories to
actions. Although suboptimal in general, useful plans can also take a
classical sequential format. This is the case in {\em conformant}
planning, where the objective is to find a sequence of actions that
achieves a goal ---I.e., reaches a state that satisfies some given
Boolean condition--- with probability $1$.  More generally, a useful
formalism for representing solutions to POMDPs is the finite-state
controller (FSC). This is a three-tuple $\langle \nodes, \selection,
\transition \rangle$ where: $\node \in \nodes$ is a set of controller
states, $\selection_\node(\action) = P(\action | \node)$ gives the
probability that the controller prescribes \action\ when in state
\node, and $\transition_\node(\action, \observation, \node') =
P(\node'|\node, \action, \observation)$ gives the probability the
controller transitions to state $\node'$, supposing we execute
\action\ in state \node\ receiving observation \observation. When
acting for finite $N$ steps, the value of a controller corresponds to
the expected cumulative reward:

\begin{equation}\label{eq:expectedvalue}
V_{\pp{FSC}}(\bstate) = \Expect \bigg{[} 
\sum_{t=0}^{N-1}  \reward(\bstate_t, \pp{FSC}_t) \mid \pp{FSC}, \bstate = \bstate_0 \bigg{]}
\end{equation}

\noindent Where $b_t$ is the belief-state at step $t$, $\pp{FSC}_t$ is
the action prescribed at step $t$, and

@@

\noindent Finally, it is
useful to note that there is a corresponding deterministic FSCs for
both sequential (e.g., conformant) and contingent plans.

>>>>

We model a process state $\state$ as the set of propositions that are
true of the state. Notationally, we have $\state \subseteq
\props$. State change is induced by application of actions. A
stochastic action $\stochAction \in \stochActions$ is applicable if
its precondition $\poss(\stochAction)$, a set of propositions, are
satisfied in the current state -- i.e., $\poss(\stochAction) \subseteq
\state$. We write $\stochActions(\state)$ for set of actions
applicable at state $\state$.  If action $\stochAction \in
\stochActions(\state)$ is applied at \state, nature chooses one
element amongst a small set of deterministic outcomes
$\detActions(\stochAction) \equiv \{\detAction_1, \ldots, \detAction_k
\}$. We denote $\mu_{\stochAction}(\detAction_i)$ the probability that
nature takes outcome $\detAct_i$, and for all \stochAction\ we require
$\sum_{\detAction_i \in \detActions(\stochAction)}
\mu_{\stochAction}(\detAction_i) = 1$. The chosen outcome has an
effect on the state given in terms of two lists of propositions. The
add-list $\add(\detAction)$ and delete-list
$\delete(\detAction)$.\footnote{If a proposition is in the add-list of
$\detAction$, then it cannot be in the delete-list and vice versa.}
If outcome $\detAction$ with $\add(\detAction) := [\prop_1,
..,\prop_n]$ and $\delete(\detAction) := [\prop_{n+1},
..,\prop_m]$ is chosen by nature when \stochAction\ is
applied at state $\state$, then the resultant state is $ ( \state \cup
\add(\detAction) ) \backslash \delete(\detAction)$ -- i.e.,
propositions from $\add(\detAction)$ are added to $\state$, and those
from $\delete(\detAction)$ are removed from $\state$.

@@

An optimal solution to a finite-horizon POMDP is a contingent plan,
and can be expressed as a mapping from observation histories to
actions. Although suboptimal in general, useful plans can also take a
classical sequential format. This is the case in {\em conformant}
planning, where the objective is to find a sequence of actions that
achieves a goal ---i.e., reaches a state that satisfies a given
Boolean condition--- with probability $1$.  Generally, whatever the
structure of a plan, its value corresponds to the expected cumulative
reward:

%% More generally, a useful
%% formalism for representing solutions to POMDPs is the finite-state
%% controller (FSC). This is a three-tuple $\langle \nodes, \selection,
%% \transition \rangle$ where: $\node \in \nodes$ is a set of controller
%% states, $\selection_\node(\action) = P(\action | \node)$ gives the
%% probability that the controller prescribes \action\ when in state
%% \node, and $\transition_\node(\action, \observation, \node') =
%% P(\node'|\node, \action, \observation)$ gives the probability the
%% controller transitions to state $\node'$, supposing we execute
%% \action\ in state \node\ receiving observation \observation. When
%% acting for finite $N$ steps from controller state $n$, the value of a
%% controller corresponds to the expected cumulative reward:

\begin{equation}\label{eq:expectedvalue}
V_{\pp{PLAN}}(\bstate, n) = \Expect \bigg{[} 
\sum_{t=0}^{N-1}  \reward(\bstate_t, \pp{PLAN}_t) \mid \pp{PLAN}, \bstate_0 = \bstate \bigg{]}
\end{equation}

\noindent Where $b_t$ is the belief-state at step $t$, $\pp{PLAN}_t$ is
the action prescribed at step $t$, and

@@

%% \noindent Finally, it is
%% useful to note that there is a corresponding deterministic FSCs for
%% both sequential (e.g., conformant) and contingent plan formats.
